The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-27 exp-resurgence.tex
Updates from Overleaf
Prepare to merge local figure changes

\textcolor{RoyalBlue}{
Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics. \textcolor{orange}{[Highlight analytic perspective more?]} Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles. In addition, we give a geometric description of the Borel plane.}
\end{abstract}
\tableofcontents
%
%
%
\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel_rescaled_ex}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel_ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral
\begin{equation}\label{int:bessel_ex}
\Phi = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du
\end{equation}
as
\[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel_ex}, up to a constant. \begin{verify}[See Mathematica document.]\end{verify}

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_{\zeta,b}^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_{\zeta,b}^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. %\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\Re(z) \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$. We will use the symbol $\sim$ to denote the asymptotic of $F$, namely we will write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
\end{defn}
\textcolor{orange}{Not all funtions are asymptotic to a power series, thus more generally, we will say a function $F$ is Poincar\'e asymptotic to a trans-monomial $e^{\lambda z}z^\tau\sum_{n=0}^Na_nz^{-n}$ for some positive $\lambda>0$ and $\tau\in(0,1)$ if 
\[\left|F - e^{\lambda z}z^{\tau}\left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\Re(z) \to \infty}\big(e^{\lambda\Re(z)}|z|^{\tau-n}\big).\]}
If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality. The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it is the function's {\em asymptotic expansion} on that sector. The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism. We will denote such map with the symbol $\aexp$. More generally, when the asymptotic expansion is taken in the direction $\theta$ at infinity, i.e. as $z\to e^{i\theta}\infty$, we will write $\aexp^\theta$.

@@

\begin{defn}\label{def:unif-gevrey-asymp}
On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
over all orders $n$ and all $z \in \Omega$. We will use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
\end{defn}
To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.

@@

Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}. These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
\begin{center}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north west] at (-\size, \size) {$z$};
\end{tikzpicture}
\end{center}
When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction. In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$. 
\begin{center}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\radius}{1}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=\ang] (\outsize, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\outsize, -\radius) -- cycle;
  \begin{scope}[violet]
    \draw (0, 0) -- (\ang:\outsize);
    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\ang:0.5) node[midway, anchor=180+\ang/2] {$\theta$};
    %%\begin{scope}[rotate=\ang]
    %%  \draw[dotted] (0, 0) -- (0, -\radius) node[anchor=90+\ang] {$r$};
    %%  \draw (\radius, -0.1) -- (\radius, 0.1);
    %%\end{scope}
    %%\fill (mark) circle (0.05);
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north west] at (-\size, \size) {$\zeta$};
\end{tikzpicture}
\end{center}

@@

%%\begin{tabular}{ll}
%%$\Phi$ & Upper-case letters without tildes represent holomorphic functions on the frequency domain.
%%\end{tabular}
\color{black}
\begin{itemize}
\item $\Phi$: upper-case letters represent holomorphic functions on the frequency domain;
\item $\tilde{\Phi}$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the frequency domain;
\item $\phi$: lower-case letters are holomorphic functions on the frequency domain. Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the spatial domain into functions on the frequency domain, we might write $\laplace_{\zeta,0}\phi=\Phi$.
\item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane. As we’ll see, the Borel transform of $\tilde{\Phi}$ is $\borel_\zeta \tilde{\Phi}=:\tilde{\phi}$; 
\item $\hat{\phi}$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}$, when it exists.  
\end{itemize}
\end{notation*}  
%between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$ we should endow $\C\lbrace\zeta\rbrace$ with th
%In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$. \textcolor{orange}{[Why not say this more generally, with $\C\llbracket z^{-1} \rrbracket$ and $\C\llbracket\zeta\rrbracket$?]} The inverse of $\borel_\zeta$ is what we call a \textit{formal Laplace transform}. \textcolor{orange}{[This seems a little weird to me, since we define the Borel transform as a formal inverse to the Laplace transform. Wouldn't it be easier to define the formal Laplace transform as a formal version of the Laplace transform, and then define the Borel transform as its inverse?]} In addition, in Section \ref{convolution} we’ll prove that the Borel transform is an algebra homomoprhism.

@@

\node[anchor=north west] at (46.5:2.46) {$\zeta=\beta$};

@@

  \draw[ietcoast!50] \p -- (0,0);
  \fill \p circle (0.7mm);

@@

\fill[ietcoast] circle (0.7mm) node[anchor=180,black, outer sep=1mm] {$\zeta = \alpha$};

>>>>

\textcolor{RoyalBlue}{
Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics. \textcolor{orange}{[Highlight analytic perspective more?]} Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles. In addition, we give a geometric description of the Borel plane.}
\end{abstract}
\tableofcontents
%
%
%
\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel_rescaled_ex}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel_ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral
\begin{equation}\label{int:bessel_ex}
\Phi = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du
\end{equation}
as
\[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel_ex}, up to a constant. \begin{verify}[See Mathematica document.]\end{verify}

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_{\zeta,b}^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_{\zeta,b}^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. %\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $F$ is {\em asymptotic} to a power series
\begin{equation}\label{series:asymp-defn}
a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
if, along each ray toward $\infty$,
\[ \left|F - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o\big(z^{-n}\big) \]
over all orders $n$. We will write
\[ F \sim \sum_{n \geq 0} a_n z^{-n} \]
to denote this relationship.
\end{defn}
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
\begin{equation}%%\label{series:asymp-defn}
\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\textcolor{magenta}{\Re(z)} \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$. \textcolor{magenta}{We will use the symbol $\sim$ to denote the asymptotic of $F$, namely we will write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]}
\end{defn}
\textcolor{orange}{Not all funtions are asymptotic to a power series, thus more generally, we will say a function $F$ is Poincar\'e asymptotic to a trans-monomial $e^{\lambda z}z^\tau\sum_{n=0}^Na_nz^{-n}$ for some positive $\lambda>0$ and $\tau\in(0,1)$ if 
\[\left|F - e^{\lambda z}z^{\tau}\left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\Re(z) \to \infty}\big(e^{\lambda\Re(z)}|z|^{\tau-n}\big).\]}
If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality. The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it is the function's {\em asymptotic expansion} on that sector. The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism. Since asymptotic expansions on overlapping sectors must agree, we can meaningfully take a function's asymptotic expansion along a ray:\textcolor{RoyalBlue}{We will denote such map with the symbol $\aexp$. More generally, when the asymptotic expansion is taken in the direction $\theta$ at infinity, i.e. as $z\to e^{i\theta}\infty$, we will write $\aexp^\theta$.}

@@

\begin{defn}\label{def:unif-gevrey-asymp}
On an open sector $\Omega$ around $\infty$, a holomorphic function $F$ is {\em uniformly $1$-Gevrey asymptotic} to a power series of the form \eqref{series:asymp-defn} if there is a constant $A \in (0, \infty)$ for which
\[ \left|F - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
over all orders $n$ and all $z \in \Omega$. We will use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
\end{defn}
To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.

@@

Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}. These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
\begin{center}
\begin{tikzpicture}
\renewcommand{\rfiber}{3}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\renewcommand{\phase}{35}
\begin{fiber}[shade, phase=\phase]
\end{fiber}
\end{tikzpicture}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north west] at (-\size, \size) {$z$};
\end{tikzpicture}
\end{center}
When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction. In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$. 
\begin{center}
\begin{tikzpicture}
\renewcommand{\rfiber}{3}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\renewcommand{\phase}{35}
\newcommand{\radius}{1}
\begin{fiber}
\fill[pwbeige!30, rotate=\phase] (\rshade, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\rshade, -\radius) -- cycle;
  \begin{scope}
    \draw[ray] (0, 0) -- (\phase:\rshade);
    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\phase:0.5) node[midway, anchor=180+\phase/2] {$\theta$};
  \end{scope}
\end{fiber}
\end{tikzpicture}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\radius}{1}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=\ang] (\outsize, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\outsize, -\radius) -- cycle;
  \begin{scope}[violet]
    \draw (0, 0) -- (\ang:\outsize);
    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\ang:0.5) node[midway, anchor=180+\ang/2] {$\theta$};
    %%\begin{scope}[rotate=\ang]
    %%  \draw[dotted] (0, 0) -- (0, -\radius) node[anchor=90+\ang] {$r$};
    %%  \draw (\radius, -0.1) -- (\radius, 0.1);
    %%\end{scope}
    %%\fill (mark) circle (0.05);
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north west] at (-\size, \size) {$\zeta$};
\end{tikzpicture}
\end{center}

@@

%%\begin{tabular}{ll}
%%$\Phi$ & Upper-case letters without tildes represent holomorphic functions on the frequency domain.
%%\end{tabular}
\color{RoyalBlue}
\begin{itemize}
\item $\Phi$: upper-case letters represent holomorphic functions on the frequency domain;
\item $\tilde{\Phi}$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the frequency domain;
\item $\phi$: lower-case letters are holomorphic functions on the frequency domain. Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the spatial domain into functions on the frequency domain, we might write $\laplace_{\zeta,0}\phi=\Phi$.
\item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane. As we’ll see, the Borel transform of $\tilde{\Phi}$ is $\borel_\zeta \tilde{\Phi}=:\tilde{\phi}$; 
\item $\hat{\phi}$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}$, when it exists.  
\end{itemize}
\color{black}
\end{notation*}
%between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$ we should endow $\C\lbrace\zeta\rbrace$ with th
%In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$. \textcolor{orange}{[Why not say this more generally, with $\C\llbracket z^{-1} \rrbracket$ and $\C\llbracket\zeta\rrbracket$?]} The inverse of $\borel_\zeta$ is what we call a \textit{formal Laplace transform}. \textcolor{orange}{[This seems a little weird to me, since we define the Borel transform as a formal inverse to the Laplace transform. Wouldn't it be easier to define the formal Laplace transform as a formal version of the Laplace transform, and then define the Borel transform as its inverse?]} In addition, in Section \ref{convolution} we’ll prove that the Borel transform is an algebra homomoprhism.

@@

\node[ietcoast!33!black, anchor=north west] at (46.5:2.46) {$\zeta = \beta$};

@@

  \draw[ietcoast] \p -- (0,0);
  \fill[ietcoast!33!black] \p circle (0.7mm);

@@

\fill[ietcoast!33!black] circle (0.7mm) node[anchor=180, outer sep=1mm] {$\zeta = \alpha$};
